Learning Augmented Joint-Space Task-Oriented Dynamical Systems: \\ A Linear Parameter Varying and Synergetic Control Approach

### 2017-10-27 paper/main_RA-L_v1.tex
Reformulated the idea of synergy space

The behavior of the JT-DS algorithm can be best understood through the lens of synergy control \cite{petrivc2013muscle}. In robotic synergy control, a robot's movements can be decomposed into a small number of synergies: principal components of the actuation-space that are sufficient to accurately recreate the desired robotic behaviors. In our case, the synergies are represented by $A_1, A_2, \dots, A_k$, and the combination of synergies used to control the system is $A(q)$ (through \eqref{eq:ds}). We are thus faced with two problems: how to determine the parameters for the synergies themselves ($A_k~\forall k\in\{1,\dots,K\}$) and how to combine the different synergies appropriately throughout different parts of the motion to yield our desired behavior (by intelligent choice of $\theta_k(q)$). Of course, we must also choose these parameters subject to the constraints laid out in \eqref{eq:first_criteria_stability}.

We propose a 3-step procedure to find these parameters. Counter-intuitively, we first find an appropriate way to combine the synergies (without knowing the synergies themselves) by learning a "synergy-space" for commanding the robot, and then identifying appropriate regions to place synergies in synergy-space. After, we will learn parameters for each synergy that would work best for each of the regions previously identified. More precisely:

@@

\item We then jointly estimate the optimal number $K$ of local synergies and the parameters of the scalar functions that determine the scheduling parameters $\theta_k(q)$ for weighting these synergies, by fitting a Gaussian Mixture Model (GMM) on the projected joint positions $\phi(q)$.

@@

\subsection{Embedding Joint Configurations in Synergy Space}
The search for a lower-dimensional representation of the joint positions stems from the desire to identify regions of \textit{similar} ``joint behaviors" (defined in Section \ref{sec:intro}), in which it would be appropriate to define synergies. It is important to understand that distances in joint space (defined as $\| \Delta q\|$) might not numerically reflect what a human intuitively perceives as the distance between joint configurations. Motor control studies have postulated that most human arm motions, be they reaching motions or following trajectories as straight/curved lines, are the result of compromising between planning a straight line in the task space and a straight line in the joint space \cite{Cruse1987humanarm,Okadome1999arm}. This suggests that human arm motion in general tends to move on a plane, and thus can be represented in such lower-dimensional space.

>>>>

The behavior of the JT-DS algorithm can be best understood through the lens of synergy control \cite{petrivc2013muscle}. In robotic synergy control, a robot's movements can be decomposed into a small number of synergies: principal components of the actuation-space that are sufficient to accurately recreate the desired robotic behaviors. In our case, the synergies are represented by $A_1, A_2, \dots, A_k$, and $A(q)$ represents the resulting motion constructed from a superposition of different synergies (through \eqref{eq:ds}).

A central question becomes how to modulate the synergies in different regions to yield our desired behavior. First, we assume that our desired behavior can be efficiently described\footnote{Given some original space $A$ and some behavior policy $\pi_A(a)$ in $A$, we say that a latent mapping $\phi(\cdot)$ and latent space $B: \{b = \phi(a) | a \in A$\}$ "efficiently describe" $\pi_A$ if there exists some policy $\pi_B(b)$ in $B$ such that we can deterministically reconstruct $\pi_A(a)$ given $\pi_B(\phi(a))$} using some sub-manifold of the joint-space, called the \emph{synergy space}. We would like to define the robot's policy in synergy space such that in different regions of the space, we will utilize different synergies. We are thus left with three problems: finding an underlying synergy-space $Z$ in which the behavior can be accurately controlled (defined by a mapping $\phi: Q \rightarrow Z$), finding a policy for modulating the synergies in different regions of the synergy space (defined by $\theta_k(q)~\forall k\in\{1,\dots,K\}$), and finding parameters for the synergies themselves (defined by $A_k~\forall k\in\{1,\dots,K\}$). Our choice of parameters must also obey the constraints laid out in \eqref{eq:first_criteria_stability}. We propose the following 3-step procedure.

@@

\item We then jointly estimate the optimal number $K$ of synergy "regions" and the parameters of the scalar functions that determine the scheduling parameters $\theta_k(q)$ for weighting these synergies, by fitting a Gaussian Mixture Model (GMM) on the projected joint positions $\phi(q)$ seen in the demonstrations.

@@

\subsection{Embedding Joint Configurations in Synergy Space}

%WE ASSUME THAT, BECAUSE OUR DEMONSTRATIONS ARE SIMILAR, POINTS IN SIMILAR REGIONS WILL HAVE SIMILAR MOTION POLICIES, SO FINDING As IS EQUIVALENT TO FINDING PRIMARY SYNERGY IN REGION, AND THEN INTERPOLATING THE SYNERGIES IN THE REGIONS IN-BETWEEN

The search for a lower-dimensional representation of the joint positions stems from the desire to identify regions of \textit{similar} ``joint behaviors" (defined in Section \ref{sec:intro}), in which it would be appropriate to define synergies. It is important to understand that distances in joint space (defined as $\| \Delta q\|$) might not numerically reflect what a human intuitively perceives as the distance between joint configurations. Motor control studies have postulated that most human arm motions, be they reaching motions or following trajectories as straight/curved lines, are the result of compromising between planning a straight line in the task space and a straight line in the joint space \cite{Cruse1987humanarm,Okadome1999arm}. This suggests that human arm motion in general tends to move on a plane, and thus can be represented in such lower-dimensional space.
